\begin{frame}
  \frametitle{Technology Used}
\textbf{Haskell.} Main programming language
\begin{itemize}
\item Pattern matching
\item GHC compiler
\end{itemize}
\smallskip
\textbf{Happy.} Parser generator for parsing user input
\begin{itemize}
\item Documentation \& less hand written code needed
\end{itemize}
\smallskip
\textbf{Latex.} Output proof
\begin{itemize}
\item Easily integrated in other Latex documents
\end{itemize}
\smallskip
\textbf{Graphviz.} Output model as graph
\begin{itemize}
\item Process and output graph for our model structures by scripting them in simple DOT language
\end{itemize}
 \end{frame}

\begin{frame}
  \frametitle{Technical Challenges}
\textbf{Implementation of caching}
\begin{itemize}
\item Caching the sets of concepts already expanded and their resulting proof or model
\item To prevent the proof/model search from non-terminating when \textit{Gamma} contains an existential restriction concept, e.g. $\exists R . \top$
\item Implementation more complicated than expected
\end{itemize}

\textbf{Extending functionality to cover individuals}
\begin{itemize}
\item So a specific individual to be expressed and reasoned with
\item Proof theory did not work with our existing program
\end{itemize}

\textbf{How addressed}
\begin{itemize}
\item Discussed theoretical issues in group meetings \& meetings with supervisor
\item Code reviews \& bug tracking system
\end{itemize}
 \end{frame}

\begin{frame}
  \frametitle{Software Development Method}
\textbf{eXtreme Programming.}
\begin{itemize}
\item Test-driven development
\item Code reviews
\item Pair programming
\end{itemize}

\textbf{Scrum.}
\begin{itemize}
\item Frequent scrum-like meetings (2 -- 3 per week)
\end{itemize}

\textbf{Crystal Clear.}
\begin{itemize}
\item Reflective improvement
\item Co-location
\end{itemize}

\textbf{Tools.}
\begin{itemize}
\item Google Code
\item Mercurial version control
\item \textit{hlint}, program similar to lint
\end{itemize}
\end{frame}


\begin{frame}
  \frametitle{Testing Method}
\textbf{Unit Testing.} Written simultaneous as code written
\begin{itemize}
\item Using HUnit, Haskell testing framework.
\item Revealed approx. 30 bugs early on or during implementation, e.g. the problem of cycles in \textit{Gamma}.
\end{itemize}
\bigskip
\textbf{Grey-box Testing.} To validate significant changes.\\
\bigskip
\textbf{Black-box Testing.} Test with large complex input cases from automatic test case generator and parsing benchmark files.\\
\bigskip
Grey-box \& black-box testing detected approx. 10 bugs

E.g. proof search did not ensure no duplicated instances of concepts at each step of the proof.
\end{frame}


\begin{frame}
  \frametitle{Plans \& Achievements}
Plan of weekly iterations composed at the beginning of the project.\\
\bigskip
Changes were made to the plan due unexpected technical problem of caching causing:
\begin{itemize}
\item An iteration dedicated to solving cycles by using caching
\item Work on caching extended to the last iteration to fix bugs
\item Iterations for extending functionality delayed by an iteration
\item Stopped extending program to cover individuals due to limited time and vast amount of change required
\end{itemize}
\bigskip
Otherwise, planned features and set tasks were completed.
\end{frame}

\begin{frame}
  \frametitle{Code Lengths}
\begin{center}
  \begin{tabular}{|l|c|}
\hline
\textbf{Component} & \textbf{Code Length (lines)} \\
\hline
Common code & 337\\
(utilities and data structures) & \\
\hline
Main & 334\\
\hline
Parser & 1111\\
\hline
Proof/Model Search & 234\\
\hline
Model Checker & 136\\
\hline
Proof Checker & 144\\
\hline
Output Model & 102\\
\hline
Output Proof & 147\\
\hline
Tests & 2338\\
\hline
Setup & 11\\
\hline
\end{tabular}
\end{center}
\end{frame}