%1
\begin{frame}
  \frametitle{Overview of the program}
  Our program is a solver for Description Logic. \\
  \pause
  \smallskip
  Description Logic is formal representation of knowledge language. \\
  With many applications in A.I., Bioinformatics, Web Semantics (OWL), \dots \\
  \pause
  \bigskip
  Our program checks if a knowledge base is satisfiable or not. \\
  By providing a model or proof otherwise. \\
\end{frame}

%2
\begin{frame}
\frametitle{Description Logic}
{\bf Question:} What is exactly Description Logic? \\
\pause
\smallskip
We will deal with $\mathcal{ALC}$ a Description Logic. \\
Its a logical language with a syntax and a semantic. \\
\pause \smallskip
Its formal syntax is defined upon two sets:  \\
\begin{itemize}
\item a set of atoms (unarys relation)
\item a set of role names (binary relation)
\end{itemize}
\pause \smallskip
Semantics is based on interpretations. An interpretation is: \\
\begin{itemize}
\item a set called domain $\Delta^{I}$.
\item a function $.^{I}$ sending concepts to subsets of $\Delta^{I}$.
\end{itemize}
\end{frame}

%3
\begin{frame}
\frametitle{Description Logic (Continuation)}
{\bf Question:} What is exactly Description Logic? \\
\pause
\bigskip
\begin{tabular}{|l|c|r|}
\hline
{\bf Syntax } & {\bf Interpretation } & {\bf Name } \\ \hline
$A$ & $A^{I} \subseteq \Delta^{I}$ & Atomic concept \\ 
$R$ & $R^{I} \subseteq \Delta^{I} \times \Delta^{I}$ & Role name \\
$\top$ & $\Delta^{I}$ & Truth \\
$\bot$ & $\emptyset$ & Falsity \\
$\neg C$ & $\Delta^{I} / C^{I}$ & Negation \\
$C \sqcap D$ & $C^{I} \cap D^{I}$ & Conjunction \\
$C \sqcup D$ & $C^{I} \cup D^{I}$ & Disjunction \\
$\forall R . C$ & $\{x | \forall y . (x,y) \in R^{I} \to y \in C^{I}\}$ & Universal rest. \\
$\exists R . C$ & $\{x | \exists y . (x,y) \in R^{I} \land y \in C^{I}\}$ & Existential rest. \\
\hline 
\end{tabular}
\end{frame}

%4
\begin{frame}
\frametitle{Description Logic (Continuation)}
The input for our software is two set of concepts: \pause
\begin{itemize}
\item Global assumptions: Concepts to be true at each point, i.e. its interpretation is $\Delta^{I}$.
\item Initial concepts: Concepts to be true at some point, i.e. its interpretation is a non-empty subset.
\end{itemize}
\bigskip
{\bf If such an interpretation exists:} We say the global assumptions together with the initial concepts are
satisfiable. We call the interpretation a {\it Model}. \\
\smallskip
\pause
{\bf Otherwise if no such an interpretation exists:} We say the global assumptions together with the initial concepts are unsatisfiable.
\end{frame}
