In this report we will give an early assessment on the project success, an update on the goals and organisation of the project. We also provide a more precise picture of the overall project structure, notably by giving a clear schedule, a description of how the project is managing its human resources and how the project deals with issues relating to ethics and the environment.

To briefly summarize, we have undertaken a few changes in our project. Notable we have combined the two first iterations into one, since it was deemed more convenient. We have successfully completed the tasks for the first iteration and we managed to complete the requirements for the second iteration with only minor readjustements in the deadlines, though we have concluded that more testing is required.

In addition to having met the requirements for the two first iterations we have added two useful features. One that allows to check proofs or models given by users, and the other that provides a more verbose output for the model and the proof checker. The main requirements and the extensions described in the inception report haven't changed and hence we are planning to extend our program to other more expressive logics in the next few iterations.

This report also describe how we deal with the management of our teams members which is essentially done by regular weekly scheduled meetings, other unscheduled meetings and through the monitoring of our progress. Our aim is to handle the diversity in skills of our members, to assign accurately and fairly tasks amongst our group members, and to ensure a dynamic workflow.

For our project there is little concern regarding ethical impact, and environmental impact. We have ensured that our project isn't in violation of any copyright law, and since our project deals with proof and model construction, there is no specific ethical issues that arise directly from the project. Simarly our project has limited impact regarding the environment, however we will put effort into computational efficiency to improve energy efficiency and we will avoid wasting paper by printing only if it is absolutely necessary.